\documentclass[10pt, a4j]{jarticle}
\usepackage[english]{babel}
\usepackage{fed2012doc}
\usepackage{here}
\usepackage{amsmath}
\usepackage{placeins}
\usepackage[dvipdfmx]{graphicx}
\usepackage{fancyhdr}
\usepackage{indentfirst}
\usepackage{cite}
\usepackage[subrefformat=parens]{subcaption}

\title{\gt 人の力を用いたロボットの誘導に関する研究\\%
{\normalsize \sf Study on robot guidance using human force}}
\author{%
Joshua SUPRATMAN, Chiba Institute of Technology\\
 $<$supratmanjoshua@gmail.com$>$ \\
}
\abstract{\fontsize{9}{10}\selectfont%
Abstract: In this paper, we present a method of attempting to induce a wheeled robotic manipulator using human force. We first discuss the orthodox method which we measure or estimate force applied on the manipulator to select a behavior. Next, we discuss the end-to-end method which estimates intension using reinforcement learning by directly taking sensor data as input and returning behavior as an output. We conduct our experiment on a simulator first before we conduct our experiment on the robot.
}
\keywords{\fontsize{9}{10}\selectfont%
Guidance, Reinforcement Learning, Intention Estimation, End-to-end Method
}

\twocolumn
\begin{document}
\maketitle

\input{background}
\input{related_works}
\input{method_of_measuring_force}
\input{behavior_selection_through}
\input{experiment_condition}
\input{proposed_procedure}
\input{conclusion}

\begin{thebibliography}{9}
\bibitem{haya}
Y. Hayashibara et al., ``Assist System for Carrying a Long Object with a Human - Analysis of a human Cooperative Behavior in the Vertical Direction -,'' Proc. 1999 IEEE/RSJ Int. Conf. on Intelligent Robots and Systems (IROS'99), 1999.

\bibitem{kosuge}
K. Kosuge, T. Hayashi, Y. Hirata, and R. Tobiyama, ``Dance partner robot -Ms DanceR-'' in IEEE/RSJ International Conference on Robots and Intelligent Systems, October 2003, pp. 345-3464.

\bibitem{yang}
Yang, Pin-Chu, et al. "Repeatable Folding Task by Humanoid Robot Worker using Deep Learning." \textit{IEEE Robotics and Automation Letters 2.2} (2017): 397-403.

\bibitem{sutton}
Sutton, R. S. and Barto, A. G. \textit{Introduction to reinforcement learning.} MIT Press, 1998.

\bibitem{mnih}
Mnih, Volodymyr, et al. "Playing atari with deep reinforcement learning." \textit{arXiv preprint arXiv:1312.5602} (2013). 

\bibitem{van}
Van Hasselt, Hado, Arthur Guez, and David Silver. "Deep Reinforcement Learning with Double Q-Learning." \textit{AAAI}. 2016.

\end{thebibliography}

\end{document}